Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-25 1607 - JMC for g2/Paper/JMC_dis.tex

\begin{figure}[tbh]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\includegraphics[width=8cm]{g2contribN}
\caption{\label{f:g2contrib} 
Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}. The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}. The pure twist-3 contribution calculated by Braun et al. \cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
}
\end{center}
\end{figure}

Another consequence of the new chiral odd term induced by the non-vanishing of
the chiral condensate on the non perturbative vacuum is that the
Burkardt-Cottingham sum rule is broken: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, h_1(x) 
    =  \frac{\mj-\mq}{\Lambda} g_T \ ,
\end{align}
where the integral over $h_1$ is related to target's tensor charge $g_T$.
Consequences:
\begin{itemize}
\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
\item Recent calcs of $g_T^{d-u}$ tensor charge are very precise - can we use this info in our plots? (to ``measure'' the quark condenstae $\langle0|\psi\bar\psi|0\rangle>$, for example? this would need an estimate of teh BC breaking, that is only availbal efrom JAM13, for all that I know.)
\end{itemize}

>>>>

\begin{figure}[tbh]
\begin{center}
\includegraphics[width=8cm]{g2contrib}
\includegraphics[width=8cm]{g2contribN}
\caption{\label{f:g2contrib} 
Different contributions to the non Wandzura-Wilczek part of the proton (left) and neutron (right) $g_2$ structure function compared to the JAM15 fit of the  $g_2-g_2^{\text{WW}}$ (solid black) \cite{JAM15}. The quark and jet contributions are shown with a dotted red and a dot-dashed green line respectively, with uncertainty bands coming form the Pavia15 fit of the transversity function \cite{Pavia15}. The unceratainty in the choice $m_q=5$ GeV and $M_q=100$ GeV is not shown. The pure twist-3 contribution calculated by Braun et al. \cite{Braun-et-al} is shown as a dashed blue line (no uncertainty estiamte was provided in teh original reference).
}
\end{center}
\end{figure}

It is interesting to consider the moments of the non Wandzura-Wilczek contribution to $g-2$,
\begin{align}
  d_N = N \int_0^1 x^N \big( g_2(x) - g_2^{WW}(x) \big) \ .
\end{align}
For a generic function $f$, let us define it's $N$-th moment as $f[N]=\int_0^1 dx\, x^{N-1} f(x)$. It is then straightforward to verify that $f^*[N] = f[N] (N-1)/N$ and  
\begin{align}
  d_N & \equiv N g_2[N+1] + (N-1) g_1[N+1] \\
  & = \frac12 \sum_q e_q^2 \bigg( N \tilde g_T^q[N+1] + \hat g_T^q[N+1]
    + \frac{N M_q-m_q}{\Lambda} h_1^q[N+1] \bigg) \ .
\end{align}
\AAcom{The notation used in JAM15 with $x^{N-1}$ for the Nth moment is pretty awkward here. Should we use $x^N$ instead?}

The zero-th moment corresponds to an extension of teh Burkhardt-Cottingham sum rule \cite{BC,Jaffe-lectures}, that appears to be broken by the non-perturbative spin-flip contribution from the jet function: 
\begin{align}
  \label{eq:BC}
  \int dx\, g_2(x) = \frac{\mj-\mq}{\Lambda} \int dx\, \frac{1}{x} h_1(x) \ .
\end{align}
This sum rule, in which the pure twist-3 part does not take part, is a consequence of the Lorentz invariance of the DIS cross section, that entails $\int_0^1 dx g_1^a(x) = \int_0^1 g_T^q(x)$. It explicitly displays the contribution from spin-flip amplitudes that is commented upon in Refs.~\cite{BC,Jaffe-lectures}, but is explicitly shown here in terms of collinear PDFs.

Consequences:
\begin{itemize}
\item Inclusive DIS become sensitive to the tensor charge; furthermore, teh BC summ rule isolates the effects due to the chiral odd part of the jet correlator. 
\item Both the jet mass $\mj$ and the tensor charge can in principle be calculated on the lattice
\item Comparison to the Burkhardt-Cottingham sum rule can provide experimental verification of lattice calculation
\item in turn these can be used to determine the size of the $h_1$ term in $g_2-g_2^{WW}$ and allow an eperimental extraction of the pure twist-3 terms.
\item Recent calcs of $g_T^{d-u}$ tensor charge are very precise - can we use this info in our plots? (to ``measure'' the quark condenstae $\langle0|\psi\bar\psi|0\rangle>$, for example? this would need an estimate of teh BC breaking, that is only availbal efrom JAM13, for all that I know.)
\end{itemize}
